\textsf{Are large language models superhuman chemists?}

### 2024-10-27 src/tex/appendix.tex
fix: change the location for data from other benchs

@@

In addition, as shown in \Cref{tab:cb_skillset} the \chembench corpus can be divided considering the different skills needed to solve the questions. The plot shows a balanced distribution of the required skills in the \chembench corpus. \Cref{tab:cb_skillset} shows an example question for each skill category.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/CB_SKILL_FIG_V1.pdf}
    \caption{\textbf{Composition of the required skills considered in the \chembench corpus.} The circular plot shows the distribution of required skills in the \chembench corpus.}
    \label{fig:cb_skillset}
\end{figure}

>>>>

While adding questions from existing benchmarks seemed to be another good source of semi-automatically generated data, we prioritize diversity of the data and avoiding data contamination while addressing the guidelines above and in \Cref{sec:desired-properties}.
Therefore, we decided to not include questions from other previous published chemistry-focused benchmarks into the \chembench corpus.

@@

In addition, as shown in \Cref{tab:chembench_corpus_cognitive} the \chembench corpus can be divided considering the different skills needed to solve the questions.

### 2024-10-27 src/tex/ms.tex
fix: change the location for data from other benchs

To ensure that the questions do not enter a training dataset, we use the same canary string as the BigBench project.
This requires that \Gls{llm} developers filter their training dataset for this canary string.\autocite{openai2024gpt4, srivastava2022beyond}
Related to this, in order to avoid data contamination we did not include data from other chemistry-focused benchmarks.
However, if in the future we decide to include them, it should not be difficult to automatically do it.

\begin{table}[!h]
    \centering
    \caption{\textbf{Overview of sources of the curated questions}. The table provides an overview of the types of sources the questions have been curated from. Detailed sources are available in the source data on GitHub. Questions without source have been curated completely from scratch. Questions based on lecture notes or URL have been curated based on content presented in those resources. All questions have been rephrased, annotated, and reviewed before being added to the corpus. The chemical preference questions are the main corpus of the semi-automatically generated group with 1001 questions of the total 1752.}
    \variable{output/sources_table.tex}
    \label{tab:sources}
\end{table}

>>>>

To ensure that the questions do not enter a training dataset, we use the same canary string as the BigBench project.
This requires that \Gls{llm} developers filter their training dataset for this canary string.\autocite{openai2024gpt4, srivastava2022beyond}

\begin{table}[!h]
    \centering
    \caption{\textbf{Overview of sources of the curated questions}. The table provides an overview of the types of sources the questions have been curated from. Detailed sources are available in the source data on GitHub. Questions without source have been curated completely from scratch. Questions based on lecture notes or URL have been curated based on content presented in those resources. All questions have been rephrased, annotated, and reviewed before being added to the corpus. Note that the chemical preference questions are the main corpus of the semi-automatically generated group with 1001 questions of the total 1752.}
    \variable{output/sources_table.tex}
    \label{tab:sources}
\end{table}
